Effects of the body force on the evacuation dynamics

### 2019-12-26 paper.tex
Update paper.tex

The maximum (realistic) compressions may be computed from the relation 
$F=k(x)\,x$ and the compressibility $k(x)$ reported in Table~\ref{table_data}. 
An ``uncomfortable'' body force of $30\,$N can address compressions in the 
range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
compressions between $0.045$ and $0.065\,$m. Thus, according to 
Table~\ref{table_data}, we may expect experimental values for $k(x)$ up to 
$1000\,$kg/s$^2$ (for $30\,$N), or, up to $1400\,$kg/s$^2$ (for $60\,$N). \\

>>>>

The maximum (realistic) compressions may be computed from the relation 
$F=k(x)\,x$ and the compressibility $k(x)$ reported in Table~\ref{table_data}. 
An ``uncomfortable'' body force of $30\,$N can address compressions in the 
range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
compressions between $0.045$ and $0.065\,$m. Thus, according to 
Table~\ref{table_data}, we may expect experimental values for $k(x)$ up to 
$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N). \\
